Essays in Computational Management Science

### 2018-08-19 Chapters/sdm-applications.tex

During the learning phase, we have generated 100 noisy images for each character. The images had 5\% of noise, i.e., 5\% of their pixels have been randomly flipped. For example, see the generated images for letter A in Figure \ref{fig-classification-training-A}. Then, we have written the classification group bitstring into the bitstring associated to each noisy image, i.e., write(bs\_image, bs\_label). For a complete image training set, see Appendix XYZ.

@@

The high noise scenario is the most interesting, because, even in a high noise level, the classifier has hit most of the characters. It has hit all images for 44 out of 62 groups and made at least one miss for the other 18 groups. The misses may be seen in details in Figure \ref{fig-classificiation-high-noise-misses}.

@@

The reward bitstring may be a positive, negative, or neutral bitstring. The positive reward bitstring is randomly generated and then only the bits related to the action will be set to 1 (see Figure \ref{fig:ttt-positive-reward-bitstring}). The negative reward bitstring is also randomly generated and then only the bits related to the action will be set to 0. Finally, the neutral reward bitstring is only a random bitstring.

@@

\caption{Positive reward bitstrings used in our reinforcement learning algorithm.
\label{fig:ttt-positive-reward-bitstrings}}
\end{figure}

>>>>

During the learning phase, we have generated 100 noisy images for each character. The images had 5\% of noise, i.e., 5\% of their pixels have been randomly flipped. For example, see the generated images for letter A in Figure \ref{fig-classification-training-A}. Then, we have written the classification group bitstring into the bitstring associated to each noisy image, i.e., write(bs\_image, bs\_label).

@@

The high noise scenario is the most interesting, because, even in a high noise level, the classifier has hit most of the characters. It has hit all images for 44 out of 62 groups and made at least one miss for the other 18 groups. The misses may be seen in details in Figure \ref{fig-classification-high-noise-misses}.

@@

The reward bitstring may be a positive, negative, or neutral bitstring. The positive reward bitstring is randomly generated and then only the bits related to the action will be set to 1 (see Figure \ref{fig:ttt-positive-reward-bitstrings}). The negative reward bitstring is also randomly generated and then only the bits related to the action will be set to 0. Finally, the neutral reward bitstring is only a random bitstring.

@@

\caption{Positive reward bitstrings used in our reinforcement learning algorithm.
\label{fig:ttt-positive-reward-bitstrings}}

\end{figure}
